The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Finish the sentence before previous commit
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@457 4525493e-7705-40b1-a816-d608a930855b

\subsection{Dealing with data-services}
DAS provided pluggable system to add a new CMS data-service. To do that we
identify appropriate APIs, input and output parameters and keys, data-service
format and mapping between data-service, DAS and other sub-systems. 
This information were stored into DAS mapping DB. For instance,
the Data Bookkeeping System (DBS) and data location system (Phedex) both
provide information about CMS data files. In former case, DBS keeps information between
files and other physics  objects, such as run and luminosity, while Phedex provides 
information about file location, such as site and details about storage elements.
Upon user request to find information about a file, based on forementioned
information we were able to identify appropriate set of
data-service APIs, look-up data, re-format their output to DAS notations and
store results into DAS cache.\footebnote{Even though we supported a data retrieval on demand
basis we also store user queries into DAS analytics DB to identify
a common patterns. Based on this information we organized a pre-fetching
strategies.}
Once data were retreived from data-services an additional step to aggregate
matched objects in DAS cache were applied. For instance in above examples
file information from DBS and Phedex systems were
retrieved. Since both data-services output contained file name as a common
key, their output where merged and final result was stored into raw-cache.
This merged (aggregated) results were shipped back to client and stored into
hot-cache (memcached) to speed up a DAS web client application. Each DAS data
object contains a standard DAS header, which identify look-up time,
request url, API, parameters and method as well as response version, expiration
time and checksum of the output.

>>>>

\subsection{Dealing with data-services}
DAS provided pluggable system to add a new CMS data-service. To do that we
identify appropriate APIs, input and output parameters and keys, data-service
format and mapping between data-service, DAS and other sub-systems. 
This information were stored into DAS mapping DB. For instance,
the Data Bookkeeping System (DBS) and data location system (Phedex) both
provide information about CMS data files. In former case, DBS keeps information between
files and other physics  objects, such as run and luminosity, while Phedex provides 
information about file location, such as site and details about storage elements.
Upon user request to find information about a file, based on forementioned
information we were able to identify appropriate set of
data-service APIs, look-up data, re-format their output to DAS notations and
store results into DAS cache.\footebnote{Even though we supported a data retrieval on demand
basis we also store user queries into DAS analytics DB to identify
a common patterns. Based on this information we organized a pre-fetching
strategies.}
Once data were retreived from data-services an additional step to aggregate
matched objects in DAS cache were applied. For instance in above examples
file information came from DBS and Phedex systems. 
Since both data-services output contained file name as a common
key, their output where merged and final result was stored into DAS cache.
This merged (aggregated) results represented a DAS data object. Each DAS data
object contains a standard DAS header, which identify look-up time,
request url, API, parameters and method as well as response version, expiration
time and checksum of the output.
